Trinity: A Language for Multi-View Architecture Description and Control

### 2017-07-27 sigplanconf-template.tex
commented out some excess template

\title{Trinity: A Language for Multi-View Architecture Description and Control\titlenote{with optional title note}}
\subtitle{Subtitle Text, if any\titlenote{with optional subtitle note}}

\authorinfo{Name1\thanks{with optional author note}}
           {Affiliation1}
           {Email1}
\authorinfo{Name2 \and Name3\thanks{with optional author note}}
           {Affiliation2/3}
           {Email2/3}

@@

\ccsdesc[500]{Software and its engineering~General programming languages}
\ccsdesc[300]{Theory of computation~Program analysis}
% end generated code

@@

\keywords
keyword1, keyword2

>>>>

\title{Trinity: A Language for Multi-View Architecture Description and Control}%\titlenote{with optional title note}}
\subtitle{Subtitle Text, if any\titlenote{with optional subtitle note}}

\authorinfo{Name1}%\thanks{with optional author note}}
           {Affiliation1}
           {Email1}
\authorinfo{Name2 \and Name3}%\thanks{with optional author note}}
           {Affiliation2/3}
           {Email2/3}

@@

%%% *** COMMENTED OUT ***
%\ccsdesc[500]{Software and its engineering~General programming languages}
%\ccsdesc[300]{Theory of computation~Program analysis}
% end generated code

@@

%%% COMMENTED OUT
%\keywords
%keyword1, keyword2
